\documentclass[11pt,letterpaper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% Formatting
\pagestyle{plain}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}
\titlespacing{\section}{0pt}{12pt}{6pt}
\titlespacing{\subsection}{0pt}{6pt}{3pt}

% Custom commands
\newcommand{\entry}[4]{%
  \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill #4 \\[2pt]
}

\newcommand{\simpleentry}[2]{%
  \textbf{#1} \hfill #2 \\[2pt]
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue,
}

\begin{document}

% Header
\begin{center}
{\LARGE\bfseries Nicholas Ford Brazeau}\\[8pt]
\vspace{1pt}
\href{mailto:nickbrazeauresearch@gmail.com}{nickbrazeauresearch@gmail.com} \quad $\bullet$ \quad \href{https://nicholasbrazeau.com}{nicholasbrazeau.com}
\end{center}

\vspace{2pt}

\section{Training \& Education}

\entry{Duke University Medical Center}{Durham, NC}{Infectious Diseases Fellowship}{July 2025 -- present}

\entry{Duke University Medical Center}{Durham, NC}{Internal Medicine Residency}{July 2023 -- June 2025}

\entry{University of North Carolina School of Medicine}{Chapel Hill, NC}{MD, Alpha Omega Alpha}{May 2023}

\entry{UNC Gillings School of Global Public Health}{Chapel Hill, NC}{PhD: Department of Epidemiology}{March 2020}
Dissertation: \textit{The Molecular, Spatial, and Genetic Epidemiology of Malaria in the Democratic Republic of the Congo}

\vspace{14pt}

\entry{Harvard College}{Cambridge, MA}{A.B. in Human Evolutionary Biology with Highest Honors}{May 2013}
Magna Cum Laude (GPA)

\vspace{18pt}

\section{Research}

\entry{Triangle Center for Evolutionary Medicine}{Durham, NC}{Research Consultant}{November 2022 -- June 2023}
\textit{Advisors:} David Rasmussen, Charles Nunn, Michael Emch \\[2pt]
Analyzed the effects of networks on agent-based infectious disease dynamic models. Developed a prototype of a generative adversarial network and variational autoencoder aimed at better understanding early pandemic propagation.

\vspace{12pt}

\entry{Imperial College London, Department of Infectious Disease Epidemiology}{London, UK}{Research Associate: COVID-19 Response Team}{April 2020 -- December 2020}
\textit{Advisors:} Azra Ghani, Robert Verity \\[2pt]
Focused on estimating the COVID-19 infection fatality ratio (IFR) from aggregate data using statistical modeling and serologic data. IFR work featured on WebMD, NewScientist, and other venues.

\vspace{12pt}

\entry{Imperial College London}{London, UK}{Visiting Researcher}{August 2019 -- December 2019}
\textit{Advisors:} Azra Ghani, Robert Verity \\[2pt]
Implemented population genetic models focused on identity by descent measures for tracing malaria relatedness.

\vspace{12pt}

\entry{UNC Gillings School of Global Public Health, Department of Epidemiology}{Chapel Hill, NC}{Research Assistant/PhD Student}{March 2016 -- March 2020}
\textit{Advisors:} Steven R. Meshnick, Jonathan J. Juliano \\[2pt]
Analyzed and monitored the spatial prevalence, emergence of drug resistance, and molecular evolution among \textit{Plasmodium falciparum} and \textit{Plasmodium vivax} using bioinformatic, epidemiological, and molecular techniques. Aim 1 of dissertation and resultant manuscript on \textit{P. vivax} in the Democratic Republic of the Congo featured on Nature Communications Editors' Highlights for Public Health and as part of the 2022 World Malaria Day Collection.

\vspace{12pt}

\entry{Kibale Chimpanzee Project, Kibale National Park}{Uganda}{Fulbright Researcher}{September 2013 -- May 2014}
\textit{Advisors:} Richard Wrangham, Zarin Machanda \\[2pt]
Expanded and continued undergraduate thesis research.

\vspace{12pt}

\entry{Kibale Chimpanzee Project}{Uganda}{Student Field \& Project Researcher}{January 2011 -- May 2013}
Examined the growth trajectories of wild chimpanzees using a non-invasive, novel photogrammetric approach. Project culminated into my Senior Honor's Thesis. Awarded approximately \$14,000 in funding.

\vspace{12pt}

\entry{Harvard Medical School}{Boston, MA}{Student Researcher}{March 2010 -- May 2013}
\textit{Advisor:} Rahmi Oklu \\[2pt]
Conducted clinical research as well as literature reviews on May-Thurner syndrome and critical limb ischemia.

\vspace{18pt}

\section{Notable Awards}

\simpleentry{Bruce Dixon Award}{May 2025}
Recipient of the institution's ``Dr. House Award,'' given to the Duke house staff member voted by peers as the best clinician.

\vspace{8pt}

\simpleentry{Gene Orringer MD./Ph.D. Excellence Award}{May 2023}
Annual award for an exceptional MD/PhD at the University of North Carolina School of Medicine. Named in honor of Eugene P. Orringer, MD.

\vspace{8pt}

\simpleentry{Kirschstein-NRSA Predoctoral MD/PhD Degree Fellowship}{January 2019 -- May 2023}
Awarded an F30 grant from the NIH to support doctoral thesis work and MD/PhD training (NIH Impact Score: 11; F30AI143172-01).

\vspace{8pt}

\simpleentry{Albert Schweitzer Fellowship}{April 2016 -- April 2017}
Community service and leadership fellowship for work as Co-Director of the Diabetes Maintenance and Prevention Program at the Open Door Clinic of Alamance County. Group visit model featured by UNC Newsroom/TraCS.

\vspace{8pt}

\simpleentry{Fulbright U.S. Student Fellowship}{September 2013 -- June 2014}
Post-undergraduate research fellowship to study the ontogenic trajectories of the wild chimpanzees with the Kibale Chimpanzee Project: Kanyawara Forest, Uganda.

\vspace{8pt}

\simpleentry{Thomas T. Hoopes Prize}{May 2013}
Annual award for exceptional undergraduate theses at Harvard College. One of the highest academic accolades bestowed on undergraduates.

\vspace{18pt}

\section{Honors \& Awards}

\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt]
\item Bruce Dixon Award \hfill May 2025
\item Gene Orringer MD./Ph.D. Excellence Award \hfill May 2023
\item Alpha Omega Alpha \hfill September 2022
\item Kevin R. Stone, MD '81 Travel Fellowship \hfill July 2022
\item Greenburg Excellence in Doctoral Research, Epidemiology Dept. Nominee \hfill March 2021
\item Kirschstein-NRSA Predoctoral MD/PhD Degree Fellowship (F30: F30AI143172-01) \hfill January 2019
\item Infectious Disease Training Grant (T32: 5T32AI070114-12) \hfill August 2018
\item University of Washington Statistical Genetics Travel Award \hfill July 2018
\item Triangle Center for Evolutionary Medicine Graduate Fellowship \hfill August 2017
\item Benjamin H. Kean Travel Fellowship in Tropical Medicine \hfill July 2017
\item International Conference on Plasmodium vivax Research Travel Award \hfill June 2017
\item Albert Schweitzer Fellowship \hfill April 2016
\item Eugene S. Mayer Honor Society for Community Service \hfill April 2016
\item IDSA Education and Research Foundation Medical Scholar \hfill April 2015
\item Alexander MD/PhD Scholarship \hfill February 2015
\item Pillsbury Award, for Best Oral Presentation in Public Health \hfill January 2015
\item Medical Scientist Training Program, Training Grant (T32: 2T32GM008719-16) \hfill August 2014
\item Fulbright U.S. Student Research Fellowship \hfill May 2013
\item Thomas T. Hoopes Prize \hfill May 2013
\item Howells Award, Most Outstanding Undergraduate Thesis in Human Evolutionary Biology \hfill May 2013
\item RSNA Cum Laude Award Winner (Poster) \hfill November 2012
\item Herchel Smith-Harvard Undergraduate Research Fellowship \hfill April 2012
\item American Society of Primates General Small Grant Recipient \hfill May 2012
\item Goelet Fund Recipient \hfill April 2012
\item Museum of Comparative Zoology Grant-in-Aid of Research Recipient \hfill February 2012
\item Harvard College Research Scholar \hfill October 2011 -- May 2012
\end{itemize}

\vspace{18pt}

\section{Teaching \& Mentoring}

\entry{University of North Carolina}{Chapel Hill, NC}{Mentoring, MD/PhD Bioinformatic \& Computational Biology Student}{June 2022 -- May 2023}
Formally mentored a MD/PhD student (Sean Connelly) within the IDEEL group on molecular surveillance, statistical genetics, and spatial analyses. Met weekly. Mentee has manuscript in preparation.

\vspace{12pt}

\entry{Ethiopian Public Health Institute}{Ethiopia}{Instructor, Applied Malaria Molecular Surveillance Workshop}{August 5--8, 2022}
Delivered lecture on identity by state and by descent with emphasis on relevance to control and eliminations efforts and led corresponding practical for national program managers and country partners. Contributed to other modules: allele frequencies, population structure, and complexity of infection as well as general workshop organization. Funded by Bill \& Melinda Gates Foundation and Imperial College London.

\vspace{12pt}

\entry{North Carolina State University}{Raleigh, NC}{Instructor, TRICEM Evolutionary Medicine Summer Institute}{May 23, 2019}
Led module using basic compartmental modeling to map the spread of hrp2-deletions in the Democratic Republic of the Congo. Discussed basic evolutionary concepts.

\vspace{12pt}

\entry{UNC Gillings School of Global Public Health}{Chapel Hill, NC}{Co-Instructor, R for Epidemiologists (EPID799-C)}{August 2018 -- December 2018}
Co-instructed an advanced R-programming course for graduate students at UNC covering functional programming, advanced graphics, multilevel modeling, and web-scraping.

\vspace{18pt}

\section{Global Public Health Experiences}

\entry{Kamuzu Central Hospital, Pediatric Unit}{Lilongwe, Malawi}{Medical Trainee}{February 2019}
Medical rotation working primarily in the pediatric ``emergency zone'' at Kamuzu Central Hospital. Aided in patient care, including diagnoses and procedures.

\vspace{12pt}

\entry{Ethiopian Public Health Institute}{Addis Ababa, Ethiopia}{Visiting Researcher}{July 2017}
Screened over 600 clinical isolates from in vivo drug efficacy studies across Ethiopia for drug resistance markers. Led a four-day module on next-generation amplicon sequencing and R-statistical software for EPHI researchers.

\vspace{18pt}

\section{Public Service, Clubs, \& Societies}

\textbf{Academic Peer Reviewer:} Evolutionary Medicine and Public Health, American Journal of Epidemiology, Parasites and Vectors, BMC Women's Health, Frontiers in Malaria (Review Editor: Antimalarial Drug Resistance)

\textbf{Academic Memberships:} American Society for Tropical Medicine and Hygiene, International Society of Evolution, Medicine, \& Public Health

\vspace{6pt}

\entry{UNC MD/PhD Case Conference}{Chapel Hill, NC}{Co-Leader}{July 2022 -- May 2023}
Organized monthly medical case-conferences for MD-PhD students as part of continuing medical education and integration of learning across the program.

\vspace{6pt}

\entry{Student Health Action Coalition (SHAC)}{Carrboro, NC}{Medical Team Senior (MTS) Staff}{November 2021 -- Present}
Served as the senior student as part of a primary care team at a student-run free clinic.

\vspace{6pt}

\entry{UNC MD/PhD Admissions Committee}{Chapel Hill, NC}{Member}{September 2018 -- December 2019}
Student admission committee member. Reviewed applications and aided in admission decisions.

\vspace{6pt}

\entry{Diabetes Maintenance and Prevention Program}{Burlington, NC}{Co-Director}{May 2015 -- June 2019}
\textit{Advisors:} John B. Buse, Laura Young \\[2pt]
Provided and coordinated free clinical services for patients with prediabetes and diabetes. Implemented shared medical appointments. Awarded Albert Schweitzer fellowship in recognition of service.

\vspace{6pt}

\entry{Gene's Knockouts, UNC MSTP Team}{Chapel Hill, NC}{Captain}{March 2016 -- July 2019}
Organized and coordinated the annual MD/PhD retreat in Wilmington, NC. Promoted team activities and events throughout the academic year.

\vspace{6pt}

\entry{Eugene S. Mayer Honor Society for Community Service}{Chapel Hill, NC}{Member}{March 2016}
Recognized for commitment to community service.

\vspace{6pt}

\entry{John B. Graham Medical Student Research Society}{Chapel Hill, NC}{Co-Vice President of Student Research Day}{January 2018 -- August 2019}
\entry{}{}{Master of Public Health \& Leave of Absence Liaison}{January 2015 -- January 2018}
Helped to organize and coordinate the 2019 student research day at UNC. Liaison for leave of absence students.

\vspace{6pt}

\entry{Evolutionary Medicine Interest Group}{Research Triangle, NC}{Co-Founder}{January 2015 -- January 2016}
Connected medical students from Duke and UNC along with public health students from UNC and veterinary students at NC State with interests in evolutionary medicine and one health. Organized meetings and lectures and promoted multi-school and interdisciplinary collaborations.

\vspace{6pt}

\entry{Kasiisi School Project}{Kibale National Park, Uganda}{Volunteer Instructor}{Summer 2012, September 2013 -- June 2014}
Raised conservation awareness and helped to enhance the educational opportunities among schools surrounding Kibale National Park.

\vspace{6pt}

\entry{Habitat for Humanity}{Cambridge, MA}{Co-Director, College Treasurer, Volunteer}{September 2010 -- January 2013}
Co-directed the Harvard Chapter of Habitat for Humanity. Co-led a spring break service trip to Macon, GA.

\vspace{6pt}

\entry{Harvard Bureau of Study Council}{Cambridge, MA}{Award Peer Tutor}{September 2012 -- January 2012}
Nominated by Harvard Professors to be a peer tutor. Tutored in evolutionary anatomy and physiology (Life Sciences 2).

\vspace{6pt}

\entry{Harvard Advising Program Office}{Cambridge, MA}{Peer Advisor Fellow}{September 2010 -- May 2013}
Peer adviser for freshman students at Harvard College.

\vspace{18pt}

\section{Other Training}

\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt]
\item GCP for Clinical Trials with Investigational Drugs, Biologics and Devices Course \hfill September 2022
\item Advanced Care Life Support (ACLS) Course, American Red Cross, Durham, NC \hfill July 2022
\item Basic Life Support (BLS) Course, American Red Cross, Raleigh, NC \hfill June 2021
\item Collaborative Institutional Training Initiative (CITI) Program \hfill May 2021
\item Institute for Healthcare Improvement Open School Online Courses \hfill September 2020, May 2021
\begin{itemize}[leftmargin=2em, itemsep=0pt, parsep=0pt]
\item Introduction to Health Care Leadership
\item Introduction to Patient Safety
\item From Error to Harm
\item Human Factors and Safety
\item Teamwork and Communication
\item Responding to Adverse Events
\item Introduction to the Triple Aim for Populations
\item Introduction to Patient-Centered Care
\item Leading Quality Improvement
\item Interpreting Data: Run Charts, Control Charts, and Other Measurement Tools
\item Testing and Measuring Changes with PDSA Cycles
\item How to Improve with the Model for Improvement
\item Introduction to Health Care Improvement
\end{itemize}
\item Responsible Conduct of Research, Chapel Hill, NC \hfill July 2018
\item MD/PhD Student Leadership Course, Chapel Hill, NC \hfill September 2017
\end{itemize}

\vspace{18pt}

\section{Interests \& Athletic Awards}

\textbf{Current Interests:} Parenting, hiking, wood-based DIY projects, cooking, reading (historical fiction, science fiction, thrillers)

\textbf{Athletic:} Harvard University, Varsity Wrestling (September 2009 -- March 2011); All State Wrestling 2008, 2009 (academic); Academic-All State Soccer 2009

\vspace{18pt}

\section{Publications}

\textbf{My PubMed:} \href{https://pubmed.ncbi.nlm.nih.gov/?term=brazeau+nf}{PubMed Link}

\textbf{ORCID:} \href{https://orcid.org/0000-0003-3976-7965}{0000-0003-3976-7965}

* Co-First Authors

\vspace{4pt}

\subsection{First and Co-First Author Publications}

\begin{enumerate}[leftmargin=*, itemsep=4pt, parsep=0pt]

\item \textbf{Brazeau, NF}; Verity, R; Jenks, S; Fu, H; Whittaker, C; Winskill, P; Dorigatti, I; Walker, PGT; Riley, S; Schnekenberg, RP; Hoeltgebaum, H; Mellan, TA; Mishra, S; Unwin, HJT; Watson, OJ; Cucunubá, ZM; Baguelin, M; Whittles, L; Bhatt, S; Ghani, AC; Ferguson, NM; Okell, LC. Estimating the COVID-19 infection fatality ratio accounting for seroreversion using statistical modelling. \textit{Communications Medicine}, 2022. PMID: 35603270.

\item \textbf{Brazeau, NF}; Mitchell, CL; Watson, OJ; Deutsch-Feldman, M; Mogran, AP; Waltmann, A; Thwai, KL; Emch, M; Wray, G; Mwandagalirwa, MK; Tshefu, AK; Likwela, JL; Parr, J; Verity, R; Edwards, J; Meshnick, SR; Juliano JJ. The Epidemiology of \textit{P. vivax} Among Adults in the Democratic Republic of the Congo: A Cross-Sectional, Nationally-Representative Survey. \textit{Nature Communications}, 2021. PMID: 34234124

\item \textbf{Brazeau, NF}*; Levinson K*; Schranz, A; Moser, K; Hollis, I; Katz, J; Bowen, A; van Duin, D; Lachewicz, A; Anderman, T; Miller, M; Juliano, JJ; Bartelt, LA. Daptomycin exposure promotes irreversible loss of daptomycin susceptibility in clinical \textit{S. epidermidis} infection co-incident with an isolated single point mutation in WalK. \textit{Evolution, Medicine, and Public Health}, 2020. PMID: 33214904

\item Verity, R*; Aydemir, O*; \textbf{Brazeau, NF}*; Watson, OJ; Hathaway, NJ; Mwandagalirwa, MK; Marsh, PW; Thwai, KL; Fulton, T; Denton, M; Morgan, AP; Parr, JB; Tumwebaze, PK; Conrad, M; Rosenthal, PJ; Ishengoma, DS; Ngondi, J; Gutman, J; Mulenga, M; Norris, DE; Moss, WJ; Mensah, BA; Myers-Hansen, JL; Ghansah, A; Tshefu, AK; Ghani, AC; Meshnick, SR; Bailey, JA; Juliano, JJ. The Impact of Antimalarial Resistance on the Genetic Structure of \textit{Plasmodium falciparum} in the DRC. \textit{Nature Communications}, 2020. PMID: 32355199.

\item Morgan, AP*; \textbf{Brazeau, NF}*; Ngasala, B; Edward, L; Denton, M; Morris, U; Filer, DL; Aydemir, O; Bailey, JA; Parr, JB; Martensson, A; Bjorkman, A; Juliano, JJ. Demography and population structure of falciparum malaria in Tanzania and Zanzibar underscores the role of importation in elimination. \textit{Malaria Journal}, 2020. PMID: 31992305

\item \textbf{Brazeau, NF}*; Assefa, A*; Mohammed, H; Seme, H; Tsadik, AG; Parr, JB; Keeler, C; Hathaway, NJ; Meshnick, SR; Bailey, JA; Kassa, M; Juliano, JJ; Woyessa, A. Pooled Deep Sequencing of Drug Resistance Loci from \textit{Plasmodium falciparum} Parasites across Ethiopia. \textit{American Journal of Tropical Medicine Hygiene}. 2019; PMID: 31436149.

\item \textbf{Brazeau NF}; Whitesell A; Doctor SM; Keeler C; Mwandagalirwa MK; Tshefu AK; Likwela JL; Juliano JJ; Meshnick SR. \textit{Plasmodium vivax} Infections in Duffy-Negative Individuals in the Democratic Republic of the Congo. \textit{American Journal of Tropical Medicine Hygiene}. 2018; PMID: 30203741.

\item Kahkoska AR*; \textbf{Brazeau NF}*; Lynch K; Kirkman MS; Largay J; Young LA; Buse JB. Implementation and Evaluation of Shared Medical Appointments for Type 2 Diabetes at a Free, Student-Run Clinic in Alamance County, North Carolina. \textit{Journal of Medical Education and Training}. 2018;2(1). pii: 032. PMCID: PMC6053275.

\item \textbf{Brazeau, NF}*; Hathaway, NJ*; Parobek, CM; Lin, JT; Bailey, JA; Lon, C; Saunders, DL, Juliano JJ. (2016) Longitudinal Pooled Deep Sequencing of the \textit{Plasmodium vivax} K12 Kelch Gene in Cambodia Reveals a Lack of Directional Selection. \textit{American Journal of Tropical Medicine \& Hygiene}. 95(6):1409-1412. PMCID: PMC5154458.

\item \textbf{Brazeau, NF}; Labbok, M; Soeters, H; Chalachala, JL; Lapika, B; Vitta, BS; Behets, F; Meshnick, SR; Yotebieng, M. (2016) Exclusive Breastfeeding and Clinical Malaria Risk in 6-month old Infants: A Cross-Sectional Study from Kinshasa, Democratic Republic of the Congo. \textit{American Journal of Tropical Medicine \& Hygiene}. 95(4):827-830. PMCID: PMC5062781.

\item \textbf{Brazeau, NF}; Pinto, E.; Harvey, H; Oliveira, G; Pomerantz, B; Wicky, S; Oklu, R. (2013) Critical Limb Ischemia. \textit{Diagnostic and Interventional Radiology}. 19(2): 173-180. PMID: 23233402.

\item \textbf{Brazeau, NF}; Harvey, H; Pinto, E; Deipolyi, A; Hesketh, R; Oklu, R. (2013) May-Thurner Syndrome: diagnosis and management. \textit{European Journal for Vascular Medicine}. 42(2): 96-105. PMID: 23485836.

\end{enumerate}

\vspace{6pt}


\subsection{Selected Co-Author Publications}
\vspace{4pt}

\begin{enumerate}[leftmargin=*, itemsep=4pt, parsep=0pt]

\item Sheppard, RJ; Watson, OJ; Pieciak, R; Lungu, J; Kwenda, G; Moyo, C; Chanda, SL; Barnsley, G; \textbf{Brazeau, NF}; Gerard-Ursin, ICG; Olivera-Mesa, D; Whittaker, C; Gregson, S; Okell, LC; Ghani, AC; MacLeod, WB; Del Fava, E; Melegaro, A; Hines, JZ; Mulenga, LB; Walker, PGT; Mwananyanda, L; Gill, CJ. Using mortuary and burial data to place COVID-19 in Lusaka, Zambia within a global context. \textit{Nat Commun}. 2023 Jun 29;14(1):3840.

\item Connelly, SV; \textbf{Brazeau, NF}; Msellem, M; Ngasala, BE; Aydemir, O; Goel, V; Niaré, K; Giesbrecht, DJ; Popkin-Hall, ZR; Hennelly, CM; Park, Z; Moormann, AM; Ong'echa, JM; Verity, R; Mohammed, S; Shija, SJ; Mhamilawa, LE; Morris, U; Mårtensson, A; Lin, JT; Björkman, A; Juliano, JJ; Bailey, JA. Strong isolation by distance and evidence of population microstructure reflect ongoing \textit{Plasmodium falciparum} transmission in Zanzibar. Under Review.

\item McCabe, R; Whittaker, C; Sheppard, RJ; Abdelmagid, N; Ahmed, A; Alabdeen, IZ; \textbf{Brazeau, NF}; Ahmed, Abd Elhameed, AE; Bin-Ghouth, AS; Hamlet, A; AbuKoura, R; Barnsley, G; Hay, JA; Alhaffar, M; Koum Besson, E; Saje, SM; Sisay, BG; Gebreyesus, SH; Sikamo, AP; Worku, A; Ahmed, YS; Mariam, DH; Sisay, MM; Checchi, F; Dahab, M; Endris, BS; Ghani, AC; Walker, PGT; Donnelly, CA; Watson, OJ. Alternative epidemic indicators for COVID-19 in three settings with incomplete death registration systems. \textit{Sci Adv}. 2023 Jun 9;9(23):eadg7676.

\item Pons-Salort, M; John, J; Watson, OJ; \textbf{Brazeau, NF}; Verity, R; Kang, G; Grassly, NC. Reassessing Reported Deaths and Estimated Infection Attack Rate during the First 6 Months of the COVID-19 Epidemic, Delhi, India. \textit{Emerging Infectious Diseases}, 2022. PMID: 35213800.

\item Mitchell, CL; Topazian, HM; \textbf{Brazeau, NF}; Deutsch-Feldman, M; Muwonga, J; Sompwe, E; Tshefu, AK; Mwandagalirwa, MK; Parr, JB; Juliano, JJ. Household Prevalence of \textit{Plasmodium falciparum}, \textit{Plasmodium vivax}, and \textit{Plasmodium ovale} in the Democratic Republic of the Congo, 2013-2014. \textit{Clinical Infectious Diseases}, 2021. PMID: 33238298.

\item McCabe, R; Kont, MD; Schmit, N; Whittaker, C; Løchen, A; Baguelin, M; Knock, E; Whittles, LK; Lees, J; \textbf{Brazeau, NF}; Walker, PG; Ghani, AC; Ferguson, NM; White, PJ; Donnelly, CA; Hauck, K; Watson, OJ. Modelling intensive care unit capacity under different epidemiological scenarios of the COVID-19 pandemic in three Western European countries. \textit{International Journal of Epidemiology}, 2021. PMID: 33837401.

\item Djaafara, BA; Whittaker, C; Watson, OJ; Verity, R; \textbf{Brazeau, NF}; Widyastuti; Oktavia, D; Adrian, V; Salama, N; Bhatia, S; Nouvellet, P; Sherrard-Smith, E; Churcher, TS; Surendra, H; Lina, RN; Ekawati, LL; Lestari, KD; Andrianto, A; Thwaites, G; Baird, JK; Ghani, AC; Elyazar, IRF; Walker, PGT. Using syndromic measures of mortality to capture the dynamics of COVID-19 in Java, Indonesia, in the context of vaccination rollout. \textit{BMC Medicine}, 2021. PMID: 34144715.

\item Deutsch-Feldman, M; Parr, JB; Keeler, C; \textbf{Brazeau, NF}; Goel, V; Emch, M; Edwards, JK; Kashamuka, M; Tshefu, AK; Meshnick, SR. The Burden of Malaria in the Democratic Republic of the Congo. \textit{Journal of Infectious Diseases}, 2021. PMID: 33057671.

\item Watson, OJ; Alhaffar, M; Mehchy, Z; Whittaker, C; Akil, Z; \textbf{Brazeau, NF}; Cuomo-Dannenburg, G; Hamlet, A; Thompson, HA; Baguelin, M; FitzJohn, RG; Knock, E; Lees, JA; Whittles, LK; Mellan, T; Winskill, P; Imperial College COVID-19 Response Team; Howard, N; Clapham, H; Checchi, F; Ferguson, N; Ghani, A; Beals, E; Walker, P. Leveraging community mortality indicators to infer COVID-19 mortality and transmission dynamics in Damascus, Syria. \textit{Nature Communications}, 2021. PMID: 33888698

\item Lin, Jessica T; Waltman, A; Moser, K; Park, Z; Na, A; Aydemir, O; \textbf{Brazeau, NF}; Gosi, P; March, P; Smith, M; Spring, M; Sok, S; Bailey, JA; Saunders, DL; Lon, C; Wojnarski, M. Selection of Cytochrome B Mutants is Rare Among \textit{Plasmodium falciparum} Patients Failing Treatment with Atovaquone-Proguanil in Cambodia. \textit{Antimicrobial Agents and Chemotherapy}, 2020. PMID: 33361308

\item Mitchell, C; \textbf{Brazeau, NF}; Deutsch-Feldman, M; Mwandagalirwa, MK; Tshefu, AK; Thwai, KL; Parr, JB; Juliano, JJ; Meshnick, SR. Under the Radar: Epidemiology of \textit{Plasmodium ovale} infections in the Democratic Republic of the Congo. \textit{Journal of Infectious Diseases}, 2020. PMID: 32766832.

\item Deutsch-Feldman, M; \textbf{Brazeau, NF}; Thwai, KL; Mwandagalirwa, MK; Tshefu, AK; Edwards, JK; Verity, R; Emch, M; Gower, EW; Juliano, JJ; Meshnick, SR. Spatial and epidemiological drivers of \textit{P. falciparum} Malaria Among Adults in the Democratic Republic of the Congo. \textit{BMJ Global Health}, 2020. PMID: 32601091.

\item Deutsch-Feldman, M; Aydemir, O; Carrel, M; \textbf{Brazeau, NF}; Bhatt, S; Bailey, JA; Kashamuka, M; Tshefu, AK; Taylor, SM; Juliano, JJ; Meshnick, SR; Verity, R. The changing landscape of \textit{Plasmodium falciparum} drug resistance in the Democratic Republic of Congo. \textit{BMC Infectious Diseases}. 2019; PMID: 31640574.

\item Boyce R; \textbf{Brazeau N}; Fulton T; Hathaway N; Matte M; Ntaro M; Mulogo E; Juliano JJ. Prevalence of Molecular Markers of Antimalarial Drug Resistance across Altitudinal Transmission Zones in Highland Western Uganda. \textit{American Journal of Tropical Medicine Hygiene}. 2019; PMID: 31436149.

\item Sá, JM; Kaslow, SR; Moraes-Barros, RR; \textbf{Brazeau, NF}; Parobek, CM; Tao, D; Salzman, RE; Gibson, TJ; Velmurugan, S; Melendez-Muniz, V; Kite, WA; Han, PK; Eastman, RT; Kim, A; Kessler, EG; Abebe, YF; James, ER; Chakravarty, S; Orr-Gonzalez, S; Lambert, L; Engels, T; Thomas, ML; Fasinu, PS; Serre, D; Gwadz, RW; Walker, L; DeConti, DK; Mu, J; Bailey, JA; Lee Sim, BK; Hoffman, SL; Fay, MP; Dinglasan, RR; Juliano, JJ; Wellems, TE. \textit{Plasmodium vivax} chloroquine resistance links to pvcrt transcription in a genetic cross. \textit{Nature Communications}, 2019; PMCID: PMC6754410.

\item \textbf{Brazeau NF}; Whitesell A; Doctor SM; Keeler C; Mwandagalirwa MK; Tshefu AK; Likwela JL; Juliano JJ; Meshnick SR. \textit{Plasmodium vivax} Infections in Duffy-Negative Individuals in the Democratic Republic of the Congo. \textit{American Journal of Tropical Medicine Hygiene}. 2018; PMID: 30203741.

\item Kahkoska AR*; \textbf{Brazeau NF}*; Lynch K; Kirkman MS; Largay J; Young LA; Buse JB. Implementation and Evaluation of Shared Medical Appointments for Type 2 Diabetes at a Free, Student-Run Clinic in Alamance County, North Carolina. \textit{Journal of Medical Education and Training}. 2018;2(1). pii: 032. PMCID: PMC6053275.

\item Parobek, CM; Parr, JB; \textbf{Brazeau, NF}; Lon, C; Chaorattanakawe, S; Gosi, P; Barnett, EJ; Norris, LD; Meshnick, SR; Spring, MD; Lanteri, CA; Bailey, JA; Saunders, DL; Lin, JT; Juliano, JJ. (2017) Partner-Drug Resistance and Population Substructuring of Artemisinin-Resistant \textit{Plasmodium falciparum} in Cambodia. \textit{Genome Biology and Evolution}. 9(6):1673-1686. PMCID: PMC5522704.

\item Parobek, CM; Lin, JT; Saunders, DL; Barnett, EJ; Lon, C; Lanteri, CA; Balasubramanian, S; \textbf{Brazeau, NF}; DeConti, DK; Garba, DL; Meshnick, SR; Spring, MD; Chuor, CM; Bailey, JA; Juliano, JJ. (2016) Selective sweep suggests transcriptional regulation may underlie \textit{Plasmodium vivax} resilience to malaria control measures in Cambodia. \textit{Proceedings of the National Academy of Sciences of the United States of America}. 113(50): E8096-E8105; PMCID: PMC5167194.

\item \textbf{Brazeau, NF}*; Hathaway, NJ*; Parobek, CM; Lin, JT; Bailey, JA; Lon, C; Saunders, DL, Juliano JJ. (2016) Longitudinal Pooled Deep Sequencing of the \textit{Plasmodium vivax} K12 Kelch Gene in Cambodia Reveals a Lack of Directional Selection. \textit{American Journal of Tropical Medicine \& Hygiene}. 95(6):1409-1412. PMCID: PMC5154458.

\item \textbf{Brazeau, NF}; Labbok, M; Soeters, H; Chalachala, JL; Lapika, B; Vitta, BS; Behets, F; Meshnick, SR; Yotebieng, M. (2016) Exclusive Breastfeeding and Clinical Malaria Risk in 6-month old Infants: A Cross-Sectional Study from Kinshasa, Democratic Republic of the Congo. \textit{American Journal of Tropical Medicine \& Hygiene}. 95(4):827-830. PMCID: PMC5062781.

\item Wrangham, RW; Koops, K; Machanda, ZP; Bernard, AB; \textbf{Brazeau, NF}; Donovan, R; Rosen, J; Wilke, C; Otali, E; Muller, MN. (2016) Matrilineal Fidelity, not Group Conformity, Explains Stability of a Chimpanzee Social Custom. \textit{Current Biology}. 26(22):3033-3037. PMID: 27839974.

\item Juliano, J; Parobek, C; \textbf{Brazeau, NF}; Ngasala, B; Randrianarivelojosia, M; Lon, C; Mwandagalirwa, K; Tshefu, A; Dhar, R; Das, B; Hoffman, I; Martinson, F; Martensson, A; Saunders, D; Kumar, N; Meshnick, SR. (2016) Pooled Amplicon Deep Sequencing of Candidate \textit{Plasmodium falciparum} Transmission Blocking Vaccine Antigens. \textit{American Journal of Tropical Medicine \& Hygiene}. 94(1): 143-6. PMCID: PMC4710419.

\item Machanda, Z; \textbf{Brazeau, NF}; Bernard, AB; Donovan, RM; Papakyrikos, AM; Wrangham, R; Smith, TM. (2015) Dental eruption in East African wild chimpanzees. \textit{Journal of Human Evolution}. 82: 137-144. PMID: 25796539.

\item \textbf{Brazeau, NF}; Pinto, E.; Harvey, H; Oliveira, G; Pomerantz, B; Wicky, S; Oklu, R. (2013) Critical Limb Ischemia. \textit{Diagnostic and Interventional Radiology}. 19(2): 173-180. PMID: 23233402.

\item \textbf{Brazeau, NF}; Harvey, H; Pinto, E; Deipolyi, A; Hesketh, R; Oklu, R. (2013) May-Thurner Syndrome: diagnosis and management. \textit{European Journal for Vascular Medicine}. 42(2): 96-105. PMID: 23485836.

\item McDermott, S; Oliveira, G; Ergul, E; \textbf{Brazeau NF}; Wicky, S; Oklu, R. (2012) May-Thurner syndrome: Can it be diagnosed on a solitary MRV study? \textit{Diagnostic and Interventional Radiology}. 19(1): 44-48. PMID: 22801870.

\end{enumerate}

\vspace{6pt}

\subsection{Publications (ICL COVID-19 Response Team)}
\vspace{4pt}

Alphabetized author list of the Imperial College COVID-19 Response Team

\begin{enumerate}[leftmargin=*, itemsep=4pt, parsep=0pt]

\item Hogan, AB; Winskill, P; Watson, OJ; Walker, PGT; Whittaker, C; Imperial College COVID-19 Response Team; Muhib, F; Hauck, K; Ferguson, NM; Ghani, AC. Within-country age-based prioritisation, global allocation, and public health impact of a vaccine against SARS-CoV-2: A mathematical modelling analysis. \textit{Vaccine}, 2021. PMID: 33933313.

\item Fu, H; Wang H; Xi, X; Boonyasiri, A; Wang, Y; Hinsley, W; Fraser, KJ; McCabe, R; Olivera Mesa, D; Skarp, J; Ledda, A; Dewé, T; Dighe, A; Winskill, P; van Elsland, SL; Imperial College COVID-19 Response Team; Imai N; Bhatia S; Ferguson NM. Database of epidemic trends and control measures during the first wave of COVID-19 in mainland China. \textit{Int J Infect Dis}, 2021 PMID: 33130212.

\item Nouvellet, P; Bhatia, S; Cori, A; Ainslie, KEC; Imperial College COVID-19 Response Team; Ferguson, NM; Donnelly, CA. Reduction in mobility and COVID-19 transmission. \textit{Nature Communications}, 2021. PMID: 33597546.

\item Thompson, HA; Imai, N; Dighe, A; Imperial College COVID-19 Response Team; Donnelly, CA; Ferguson, NM. SARS-CoV-2 infection prevalence on repatriation flights from Wuhan City; China. \textit{J Travel Med}, 2020. PMID: 32830853.

\item Unwin, HJT; Mishra, S; Bradley, VC; Gandy, A; Mellan, TA; Coupland, H; Ish-Horowicz, J; Vollmer, MAC; Whittaker, C; Filippi, SL; Xi, X; Monod, M; Ratmann, O; Hutchinson, M; Valka, F; Zhu, H; Hawryluk, I; Milton, P; Imperial College COVID-19 Response Team; Ghani, AC; Ferguson, NM; Riley, S; Donnelly, CA; Bhatt, S; Flaxman, S. State-level tracking of COVID-19 in the United States. \textit{Nat Comm}, 2020. PMID: 33273462.

\item Grassly, NC; Pons-Salort, M; Parker, EPK; White, PJ; Ferguson, NM; Imperial College COVID-19 Response Team. Comparison of molecular testing strategies for COVID-19 control: a mathematical modelling study. \textit{Lancet Infect Dis}, 2020. PMID: 32822577.

\item Dighe, A; Cattarino, L; Cuomo-Dannenburg, G; Skarp, J; Imai, N; Bhatia, S; Gaythorpe, KAM; Imperial College COVID-19 Response Team; Ghani, AC; Donnelly, CA; Ferguson, NM; Riley, S. Response to COVID-19 in South Korea and implications for lifting stringent interventions. \textit{BMC Med}, 2020. PMID: 33032601.

\item Hogan AB; Jewell BL; Sherrard-Smith E; Vesga JF; Watson OJ; Whittaker C; Hamlet A; Smith JA; Winskill P; Verity R; Baguelin M; Lees JA; Whittles LK; Imperial College COVID-19 Response Team; Ferguson NM; Okell LC; Churcher TS; Arinaminpathy N; Ghani AC; Walker PGT; Hallett TB. Potential impact of the COVID-19 pandemic on HIV; tuberculosis; and malaria in low-income and middle-income countries: a modelling study. \textit{Lancet Glob Health}, 2020. PMID: 32673577.

\item Walker PGT; Whittaker C; Watson OJ; Baguelin M; Winskill P; Hamlet A; Djafaara BA; Cucunubá Z; Olivera Mesa D; Green W; Thompson H; Nayagam S; Imperial College COVID-19 Response Team; Lalloo DG; Ferguson NM; Ghani AC. The impact of COVID-19 and strategies for mitigation and suppression in low- and middle-income countries. \textit{Science}, 2020. PMID: 32532802.

\item Jeffrey B; Walters CE; Imperial College COVID-19 Response Team; Ferguson NM; Donnelly CA; Riley S. Anonymised and aggregated crowd level mobility data from mobile phones suggests that initial compliance with COVID-19 social distancing interventions was high and geographically consistent across the UK. \textit{Wellcome Open Research}, 2020. PMID: 32954015.

\end{enumerate}

\end{document}
