---
title: "Using Statistical Modeling to win a NFL KO Pool"
author: "Nicholas F. Brazeau"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    highlight: textmate
    theme: lumen
    toc: yes
    toc_float: yes
    toc_depth: 3
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center', fig.width = 6, fig.height = 6)
knitr::opts_knit$set(root.dir = here::here(""))
```

# Introduction
Admittedly, I am a terrible sports fan. However, I do enjoy competition and the opportunity to participate in a little "smack talk" with family and friends. Every year, family, friends, and folks from my childhood community come together to play a game of "NFL Pool Knockout". The rules are relatively simple: each participant picks one NFL team each week - if the team wins, you advance. Each team can only be selected once during the season. Ties count as losses. 



$18! ~\approx 6.4e15$


### Dependencies
```{r, fold=FALSE}
#remotes::install_github("nickbrazeau/nflKOSA")
library(nflKOSA)
library(tidyverse)
library(nflplotR)
```



## Run what you brung

```
  nflplotR::valid_team_names()
nflplotR::geom_nfl_logos(aes(team_abbr = team), width = 0.065, alpha = 0.7) +

```